%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
\definecolor{awesome}{HTML}{067A85}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{Ashkan} \headerlastnamestyle{Shakiba} \\
	\vspace{2mm}
	\textcolor{awesome}{Software Developer{\enskip\cdotp\enskip}Computer Eng. Student} \\
	\vspace{2mm}
	{\faEnvelope\ AshkanShakiba11@gmail.com} | {\faMobile\ (+98) 9039103980} | {\faMapMarker\ Tehran, Iran} \\
	{\href{https://linkedin.com/in/AshkanShakiba}{\faLinkedin\ AshkanShakiba}} | {\href{https://github.com/AshkanShakiba}{\faGithub\ AshkanShakiba}} | {\href{skype:live:.cid.ab6ac0e95ae8e6eb?chat}{\faSkype\ live:.cid.ab6ac0e95ae8e6eb}}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Technical Skills}
\begin{cventries}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
		\vspace{0.25mm}Programming Languages:  & {\skill{ Python, Java, JavaScript, TypeScript, Kotlin, C}} \\
		\vspace{0.25mm}Database Management:  & {\skill{ SQL, MySQL, PostgreSQL, elasticsearch, redis}} \\
		\vspace{0.25mm}Backend Development:  & {\skill{ Django, Django REST framework, CherryPy}} \\
		\vspace{0.25mm}Frontend Development:  & {\skill{ HTML, CSS, Angular, Flutter, Scss}} \\
		\vspace{0.25mm}DevOps and Testing:  & {\skill{ Git, Docker, Selenium}} \\
		\vspace{0.25mm}Operating Systems:  & {\skill{ Linux (Ubuntu), Windows}} \\
		\vspace{0.25mm}Software Engineering:  & {\skill{ Agile and Scrum, Design Patterns, Testing}} \\
		\vspace{0.25mm}Programming Expertise:  & {\skill{ Data Structures and Algorithms, Object-oriented Programming, Microservices}} \\
		\vspace{0.25mm}Also familiar with:  & {\skill{ Golang, Blockchain and Cryptocurrencies, Android Development, React, kibana}} \\
		\end{tabular}}}
	{}
	{}
	{}
\end{cventries}
\vspace{-7mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Work Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Work Experience}
\begin{cventries}
	\cventry
	{\textbf{Software Developer}}
	{Tabdeal Cryptocurrency Exchange}
	{Tehran, Iran}
	{Sep 2022 – Jan 2023}
	{\begin{cvitems}
		\vspace{1mm}
		\item[] {\hspace{-9mm} Website: \href{https://tabdeal.org}{\textcolor{awesome}{https://tabdeal.org}}}
		\vspace{1mm}
		\item {Technologies: Python, Django, Django REST framework, MySQL, PostgreSQL, etc.}
		\vspace{1mm}
		\item {Develop services to manage and transfer cryptocurrencies, such as wallets and node handlers}
	\end{cvitems}}
	\cventry
	{\textbf{Backend Developer}}
	{Gradient Data Processing (Technical Team of Mobin Sarmaye)}
	{Tehran, Iran}
	{Feb 2022 – Aug 2022}
	{\begin{cvitems}
		\vspace{1mm}
		\item {Technologies: Python, CherryPy, elasticsearch, kibana, pandas, NumPy, matplotlib, PIL, Selenium, etc.}
		\vspace{1mm}
		\item {Develop services to explore and receive data, process it, and store it in an efficient way}
		\vspace{1mm}
		\item {Implement multiple backend services for a financial explorer and its club}
	\end{cvitems}}
	\cventry
	{\textbf{Frontend Trainee}}
	{CodeStar Bootcamp (at Mohaymen ICT)}
	{Tehran, Iran}
	{Jul 2021 – Sep 2021}
	{\begin{cvitems}
		\vspace{1mm}
		\item {Technologies: Angular, TypeScript, Scss}
	\end{cvitems}}
	\cventry
	{\textbf{Software Developer}}
	{Freelancer}
	{Remote}
	{Sep 2020 – Feb 2022}
	{\begin{cvitems}
		\vspace{1mm}
		\item {Technologies: C, Java, JavaScript, Angular}
		\vspace{1mm}
		\item {Develop multiple projects such as \href{https://github.com/AshkanShakiba/Pexeso}{\textcolor{awesome}{Pexeso}}, \href{https://github.com/AshkanShakiba/Joojle}{\textcolor{awesome}{Simple Search Engine}}, etc.}
	\end{cvitems}}
\end{cventries}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{\textbf{Bachelor\textquotesingle{}s degree in Computer Engineering}}
	{Amirkabir University of Technology (Tehran Polytechnic)}
	{Tehran, Iran}
	{Sep 2020 – Current}
	{\begin{cvitems}
		\vspace{1mm}
		\item[] {\hspace{-9mm} GPA: 18.50 (out of 20)}
		\vspace{1mm}
		\item[] {\hspace{-9mm} Important Grades (out of 20):}
		\vspace{1mm}
		\item {Fund. of Programming: 20}
		\item {Advanced Programming: 20}
		%\item {Discrete Mathematics: 18}
		\item {Data Structures and Algorithms: 19.3}
		\item {Logic Circuits: 19.2}
		\item {Computer Architecture: 18.8}
		\item {Principles of Artificial Intelligence: 18.75}
		\item {Software Engineering: 20}
		\item {Mobile Programming: 20}
	\end{cvitems}}
%	\cventry
%	{\textbf{High School Diploma in Mathematics and Physics}}
%	{National Organization for Development of Exceptional Talents (Sampad)}
%	{Bojnord, Iran}
%	{Sep 2017 – Sep 2020}
%	{\begin{cvitems}
%		\vspace{1mm}
%		\item[] {\hspace{-9mm} GPA: 19.35 (out of 20)}
%	\end{cvitems}}
\end{cventries}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2mm}
\cvsection{Projects}
\begin{cventries}
	\cventry
	{\textbf{B2B phone charge system}}
	{Bell}
	{Django, Django REST f. , PostgreSQL}
	{\href{https://github.com/AshkanShakiba/Bell}{\faGithub\ AshkanShakiba/Bell}}
	{\begin{cvitems}
		\vspace{1mm}
		\item[] {\hspace{-9mm} Challenges:}
		\vspace{1mm}
		\item {Implement ACID transactions}
		\vspace{1mm}
		\item {Develop REST API and document it}
		\vspace{1mm}
		\item {Using Scout APM to monitor services}
	\end{cvitems}}
	\vspace{0mm}
	\cventry
	{\textbf{Journalism Application}}
	{Kyusk}
	{Django, PostgreSQL}
	{\href{https://github.com/AshkanShakiba/Kyusk}{\faGithub\ AshkanShakiba/Kyusk}}
	{\begin{cvitems}
		\vspace{1mm}
		\item[] {\hspace{-9mm} Challenges:}
		\vspace{1mm}
		\item {Database Management}
		\vspace{1mm}
		\item {Develop views and design UI}
	\end{cvitems}}
	\vspace{0mm}
	\cventry
	{\textbf{Blog API}}
	{Paragraph}
	{Django, Django REST f. , PostgreSQL}
	{\href{https://github.com/AshkanShakiba/Paragraph}{\faGithub\ AshkanShakiba/Paragraph}}
	{\begin{cvitems}
		\vspace{1mm}
		\item[] {\hspace{-9mm} Challenges:}
		\vspace{1mm}
		\item {Database Management}
		\vspace{1mm}
		\item {Develop REST API and document it}
	\end{cvitems}}
	\vspace{0mm}
	\cventry
	{\textbf{Advanced Programming Final Project}}
	{Clash Royale}
	{Java, JavaFX, MySQL}
	{\href{https://github.com/AshkanShakiba/Clash-Royale}{\faGithub\ AshkanShakiba/Clash-Royale}}
	{\begin{cvitems}
		\vspace{1mm}
		\item[] {\hspace{-9mm} Challenges:}
		\vspace{1mm}
		\item {Develop game using MVC architecture}
		\vspace{1mm}
		\item {Database Management}
		\vspace{1mm}
		\item {Graphic Design}
	\end{cvitems}}
	\vspace{0mm}
	\cventry
	{\textbf{Android E-book Reader Application}}
	{Bookzy}
	{Android, Kotlin}
	{\href{https://github.com/maryam-kermanshahani2001/Bookzy}{\faGithub\ AshkanShakiba/Bookzy}}
	{\begin{cvitems}
		\vspace{1mm}
		\item[] {\hspace{-9mm} Challenges:}
		\vspace{1mm}
		\item {Develop reader's functionalities and features}
		\vspace{1mm}
		\item {Using firebase cloud as object storage service}
		\vspace{1mm}
		\item {Graphic Design}
	\end{cvitems}}
	\vspace{-3mm}
\end{cventries}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Teaching Assistant Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{2mm}
\cvsection{Teaching Assistant Experience}
\begin{cvhonors}
	\cvhonor
	{Software Engineering}
	{Teaching Assistant under the supervision of Dr. Alirezaei}
	{AUT, UT}
	{Feb 2023}
	\cvhonor
	{Fundamentals of Programming}
	{Teaching Assistant under the supervision of Mr. Alvani}
	{AUT}
	{Feb 2022}
	\cvhonor
	{Advanced Programming}
	{Teaching Assistant under the supervision of Dr. Zeinali and Dr. Kalbasi}
	{AUT}
	{Feb 2022}
	\cvhonor
	{Advanced Programming}
	{Workshop Documentation Author under the supervision of Mr. Hoseini}
	{AUT}
	{Jul 2021}
	\cvhonor
	{Fundamentals of Programming}
	{Teaching Assistant under the supervision of Dr. Zeinali}
	{AUT}
	{Sep 2021}
\end{cvhonors}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Volunteering
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{2mm}
\cvsection{Volunteering}
\begin{cventries}
	\cventry
	{\textbf{Official Member}}
	{Students'​ Scientific Chapter (SSC)}
	{Tehran, Iran}
	{Aug 2021 – Mar 2023}
	{Members of the Students' Scientific Chapter are annually chosen in an election and with the vote of Amirkabir Univ. of Tech. Computer Eng. Dept.'s students.
	I am selected as an official member and head of the competition commission.
	SSC has always held different events such as \href{http://linuxfest.aut.ac.ir/}{\textcolor{awesome}{LinuxFest (Linux and open source festival)}}, \href{https://icpc.aut.ac.ir/}{\textcolor{awesome}{Amirkabir
	Collegiate Programming Contest}}, Amirkabir Artificial Intelligence Summer Summit, Data Mining Challenge, \href{https://gamecraft.ce.aut.ac.ir/}{\textcolor{awesome}{GameCraft}} and etc.
	Also, SSC has presented talks, courses, and other programs to help students interact with the industry.}
\end{cventries}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Languages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Languages}
\begin{cvhonors}
	\cvhonor
	{Persian}
	{Mother tongue}
	{}
	{Native}
	\cvhonor
	{English}
	{Listening B2, Reading B2, Writing B2, Speaking B2}
	{}
	{Advanced}
\end{cvhonors}
\ 
\end{document}